\songtitle{Barrels of Whiskey}{The O'Reillys and the Paddyhats}{2016}

\guitarchord{Em}
\guitarchord{G}
\guitarchord{D}
\guitarchord{C}
\guitarchord{Am}

\begin{guitar}
	
	\songsection{Verse 1}
	As I [Em]stepped out me house, I [G]saw this man named [D]Clyde. 
	He [Em]took me by the hand saying: "I'll [C]take you [D]for a [Em]ride." 
	I [C]said: "I cannot go there there're [Em]things to get [D]done." 
	He [C]said: "Boy you must, 'cause I [Em]ain't [D]got a [Em]son.
	[Em]There's a little secret that [G]no one should [D]know.
	[Em]Deep into the forest, we [C]both [D]gotta [Em]go.
	I [C]show you the way, I [Em]earn my daily [D]bread,
	But [C]dare not to reveal it or you're [Em]gonna lose your head!"[D]{}
	
	\songsection{Chorus}
	I make [Em]barrels of [C]whiskey; it [G]ain't no cham[D]pagne.
	It's [Em]served in our [C]brothels to [G]keep away the [D]pain! 
	[Am]What I [Em]share with [Am]you my [Em]lad, is the [Am]biggest [Em]secret I've [C]ever [D]had. 
	I make [Em]barrels of [C]whiskey; it [G]ain't no cham[D]pagne.
	Its [Em]served in our [C]brothels to [G]keep a[D]way the [Em]pain! 
	
	\songsection{Instrumental}
	{\footnotesize\begin{tabular}{l|l|l|l}
			(Em) & Em & G & D \\
			Em & Em & C D & Em\\
			G & G & D & D\\
			Em & Em & C D & Em 
	\end{tabular}}
	
	\songsection{Verse 2}
	See the [Em]soldiers at war, [G]on the battle[D]field.
	They've [Em]got more than a gun, my [C]whiskey [D]is their [Em]shield.
	[Em]Look at the crippled, the [G]wounded down the [D]street.
	A [Em]passport to hell and a [C]bottle [D]to their [Em]feet.
	You [C]don't leave a child or [Em]sweetheart be[D]hind.
	This [C]is our secret vow so [Em]boy don't be [D]blind.
	\pagebreak
	
	\songsection{Chorus}
	I make [Em]barrels of [C]whiskey; it [G]ain't no cham[D]pagne.
	It's [Em]served in our [C]brothels to [G]keep away the [D]pain!
	[Am]What I [Em]share with [Am]you my [Em]lad, is the [Am]biggest [Em]secret I've [C]ever [D]had.
	I make [Em]barrels of [C]whiskey; it [G]ain't no cham[D]pagne.
	[Am]What I [Em]share with [Am]you my [Em]lad, [Am]what I [Em]share with [D]you... 
	
	\songsection{Chorus} \songsnippet{I make barrels of whiskey...}
\end{guitar}
