\songtitle{Diggy Diggy Hole}{The Yogscast}{2014}

\guitarchord{Em}
\guitarchord{C}
\guitarchord{G}
\guitarchord{D}
\guitarchord{B}
{\footnotesize(Capo 2nd fret)}

\begin{guitar}
	
	\songsection{Verse 1}
	[Em]Brothers of the mine rejoice! [C]Swing, [G]swing, [Em]swing with me.
	[Em]Raise your pick and raise your voice! [C]Sing, [G]sing, [Em]sing with me.
	[Em]Down and down in[D]to the deep. [C]Who knows what we'll [G]find beneath?
	[Em]Diamonds, rubies, [D]gold and more, [B]hidden in the mountain store.
	
	\songsection{Pre-Chorus}
	[C]Born under[G]ground, [D]suckled from a teat of stone.
	[C]Raised in the [G]dark, the [D]safety of our mountain home.
	[C]Skin made of [G]iron, [B]steel in our [C]bones.
	To [C]dig and dig makes us free. [D]Come on, brothers, sing with me!
	
	\songsection{Chorus}
	[Em]I am a [G]dwarf and I'm [D]digging a [C]hole
	[C]Diggy diggy [G]hole, [C]diggy diggy [B]hole
	[Em]I am a [G]dwarf and I'm [D]digging a [C]hole
	[C]Diggy diggy [G]hole, [B]diggy diggy [Em]hole
	
	\songsection{Verse 2}
	The sunlight will not reach this low - deep, deep in the mine.
	Never seen the blue moon glow - dwarves won't fly so high.
	Fill a glass and down some meat. Stuff your bellies at the feast.
	Stumble home and fall asleep, dreaming in our mountain keep.
	
	\songsection{Pre-Chorus}
	Born underground, grown inside a rocky womb
	The earth is our cradle; the mountain shall become out tomb
	Face us on the battlefield; you will meet your doom
	We do not fear what lies beneath. We can never dig too deep
	
	\songsection{Chorus} \songsnippet{I am a dwarf...} (x2)
	
	\songsection{Pre-Chorus} \songsnippet{Born underground, suckled from a teat of stone...}
	
	\songsection{Chorus} \songsnippet{I am a dwarf...} (x2)
\end{guitar}