\songtitle{Finnegan's Wake}{Traditional}{$\sim$1850}

\guitarchord{C}
\guitarchord{Am}
\guitarchord{F}
\guitarchord{G}

\begin{guitar}
	\songsection{Verse 1}
	Tim [C]Finnegan lived in [Am]Walkin Streen,
	A [F]gentle Irishman, [G]mighty odd.
	He [C]had a brogue both [Am]rich an sweet
	An' to [F]rise in the world he [G]carried a [C]hod.
	You [C]see he'd a sort of a [Am]tippler's way 
	With the [C]love for the liquor poor [Am]Tim was born
	And to [C]help him on his [Am]way each day, 
	He'd a [F]drop of the craythur [G]every morn.[C]{}
	
  \begin{chorus}{Chorus}
	[C]Whack fol the daw now [Am]dance to yer partner
	[F]'Round the floor yer [G]trotters shake.
	[C]Wasn't it the [Am]truth I told you?
	[F]Lots of fun at [G]Finnegan's [C]Wake.%
  \end{chorus}
	
	\songsection{Verse 2}
	One morning Tim got rather full,
	His head felt heavy which made him shake
	Fell from a ladder and broke his skull,
	And they carried him home his corpse to wake
	Rolled him up in a nice clean sheet, 
	And laid him out upon the bed
	A bottle of whiskey at his feet 
	And a barrel of porter at his head
	
	\songsection{Chorus} \songsnippet{Whack fol the dah now dance to yer partner...}
	
	\pagebreak
	
	\songsection{Verse 3}
	His friends assembled at the wake 
	And Mrs. Finnegan called for lunch
	First she brought in tay and cake, 
	Then pipes, tobacco and whiskey punch
	Biddy O'Brien began to cry: 
	"Such a nice clean corpse did you ever see?
	Tim mavourneen, why did you die?" 
	"Will ye hould your gob?", said Paddy McGee
	
  \begin{chorus}{Chorus}
	[C]Whack fol the daw now [Am]dance to yer partner
	[F]'Round the floor yer [G]trotters shake.
	[C]Wasn't it the [Am]truth I told you?
	[F]Lots of fun at [G]Finnegan's [C]Wake.%
  \end{chorus}
	
	\songsection{Verse 4}
	Then Maggie O'Conor took up the job. 
	"Biddy", says she, "you're wrong, I'm sure"
	Biddy gave her a belt in the gob 
	And left her sprawling on the floor.
	Then the war did soon engage, 
	T'was woman to woman and man to man.
	Shilelagh low was all the rage 
	And a row and a ruction soon began.
	
	\songsection{Chorus} \songsnippet{Whack fol the dah now dance to yer partner...}
	
	\songsection{Verse 5}
	Mickey Maloney ducked his head 
	When a bucket of whiskey flew at him
	It missed and, falling on the beg,
	The liquor scattered over Tim.
	Bedad he revives, see how he rises,
	Timothy rising from the bed.
	Said: "Whirl your whiskey around like blazes, 
	Thanam 'on dhoul, do ye think I'm dead?"
	
	\songsection{Chorus} \songsnippet{Whack fol the dah now dance to yer partner...} (x2)
\end{guitar}
