\songtitle{Hoist Up The Thing}{The Longest Johns}{2020}

\guitarchord{D}
\guitarchord{G}
\guitarchord{A}
\guitarchord{Bflat}
\guitarchord{Gm}
\guitarchord{F}

\begin{guitar}
	\songsection{Verse 1}
	[D]Fresh out of college, with [G]grades straight from [D]Hell
	I [D]browsed for a trade at which [A]I could excel
	An [D]ad for a ship in [G]need of some [D]manning
	[D]Men, sails, and purpose, but [A]lacking a [D]captain
	
	[G]What luck, says I, to [D]find such good fortune!
	A [A]few white lies later, I [D]ran down the pier,
	[G]Bought me a coat and a [D]cutlass or two,
	[A]Jumped on the deck, and I yelled at the crew:
	
	\songsection{Chorus}
	[G]Hoist up the thing! [D]Batten down the whatsit!
	[A]What's that thing spinning? Some[D]body should stop it!
	[G]Turn hard to port! (That's not [D]port) Now I've got it!
	[A]Trust me, I'm in con[D]trol!
	
	\songsection{Verse 2}
	I can't sing the shanties, it has to be said
	And all of that grog just goes right to my head
	Whale meat is gross and I miss a girl's laugh
	Five weeks at sea, even Dave seems a catch!
	
	\songsection{Chorus} \songsnippet{Hoist up the thing! Batten down the whatsit! ...}
	
	\songsection{Verse 3}
	We've [D]hit icy waters, no [G]land to be [D]seen
	The [D]food's getting low and the [A]beer has gone green
	There's [Bb]murmurs of discontent [Gm]under the [D]deck
	If [D]I don't act fast, it [A]could be my [D]neck!
	\pagebreak
	So [D]pull up the charts and those [G]weird gold ma[D]chines
	I [D]see what it says but no [A]clue what it means!
	Just [D]pull on some levers and [G]yank on some [D]chains
	[D]Feign a bad back 'til we've [A]landed again
	
	\songsection{Chorus} \songsnippet{Hoist up the thing! Batten down the whatsit! ...} (x3)
	
	[G]Hoist up the thing! [D]Batten down the whatsit!
	[A]What's that thing spinning? Some[D]body should stop it!
	[G]Turn hard to port! (This is [D]Sherry!) Now I've got it!
	[A]Trust me, I'm in con[D]trol! 
	[A]Trust me, I'm [A7]in con[D]trol!
\end{guitar}