\songtitle{I'm Mr. Meeseeks}{Royish Good Looks}{2017}
% I used chordify to extract the chords

\adjustboxDefault{%
\guitarchord{D}
\guitarchord{A}
\guitarchord{Bm}
\guitarchord{G}
\guitarchord{E}
\guitarchord{B}
\guitarchord{Csharpm}}
\capoEN{1}

\begin{guitar}
	\songsection{Chorus}
	[D]I'm Mr. Meeseeks,[A] look at me! [Bm]I'm Mr. Meeseeks! [G]Yes, sir-ee!
	You [D]make a request, the [A]meeseeks fulfills the re[Bm]quest and then it stops ex[G]isting. (Uh, okay!)
	[D]I'm Mr. Meeseeks,[A] look at me! [Bm]I'm Mr. Meeseeks! [G]Yes, sir-ee!
	I [D]have to fulfill my [A]purpose so I can go a[Bm]way,
	So I can go a[G]way. Existence is pain.
	
	\songsection{Verse 1}
	[D] Re[A]member to square your [Bm]shoulders Jerry [G]{}
	Choke up on the [D]club;[A] you know you gotta do [Bm]both. Just [G]choke up on the club.
	
	\songsection{Chorus} \songsnippet{I'm Mr. Meeseeks, look at me! I'm Mr. Meeseeks! Yes, sir-ee! (...)}
	
	\songsection{Verse 2}
	Everybody [D]stop! You mind if we get [Bm]back to the task at [G]hand? 
	[D]Meeseeks don't usually [A]have to exist this [Bm]long. It's getting [G]weird.
	
	\songsection{Chorus} \songsnippet{I'm Mr. Meeseeks, look at me! I'm Mr. Meeseeks! Yes, sir-ee! (...)}
	
	\songsection{Bridge}
	[Bm] I can't take it [G]anymore!
	I [D]just wanna die. I [A]just wanna die.
	We all wanna die; we're meeseeks! 
	Why did you even rope me into this?
	(Cause) he roped me into this. Well, him over there, 
	He roped me into this. Well, he roped me into this. 
	What about me? He, he roped me into this.
	Well, that one over there roped me into this.
	\pagebreak
	\songsection{Chorus}
	[Bm]I'm Mr. Meeseeks,[G] look at me! [D]I'm Mr. Meeseeks! [A]Yes, sir-ee!
	[Bm]I'm Mr. Meeseeks,[G] look at me! [D]I'm Mr. Meeseeks! [A]Yes, sir-ee!
	I [Bm]have to fulfill my [G]purpose so I can go a[D]way,
	So I can go a[G]waa[B]aay
	
	\songsection{Chorus}
	[E]I'm Mr. Meeseeks,[B] look at me! [C#m]I'm Mr. Meeseeks! [A]Yes, sir-ee!
	You [E]make a request, the [B]meeseeks fulfills the re[C#m]quest and then it stops ex[A]isting. (Uh, okay!)
	[E]I'm Mr. Meeseeks,[B] look at me! [C#m]I'm Mr. Meeseeks! [A]Yes, sir-ee!
	I [E]have to fulfill my [B]purpose so I can go a[C#m]way,
	So I can go a[A]way. Existence is pain.[E]{}
\end{guitar}