\songtitle{Kill Yourself}{Bo Burnham}{2016}
% The release date refers to the release of Make Happy, though I think it was released earlier (I think the song was also in Words Words Words...)

\guitarchord{F}
\guitarchord{Dm}
\guitarchord{Bflat}
\guitarchord{C}
\guitarchord{Gm}

\begin{guitar}
	\songsection{Verse 1}
	[F] Have you ever felt sad or lonley?[Dm] Have you ever felt two feet tall?
	[Bb] Have you ever thought: "Man, if only[C] I was anybody else at all."
	[F] They like to kick you[Dm] when times get rough
	[Bb] And you give your all[C] but it's not enough.
	
	\songsection{Bridge}
	And [Bb]sticks and stones might [C]break your bones
	But [F]words can [Gm]break your [Dm]heart.[C]{}
	And [Bb]if you don't know [C]where to go
	I'll [F]show you [Gm]where to [Dm]start.[C]{}
	
	\begin{highlightbar}
		\songsection{Chorus}
		[F]Kill yourself.[Dm] It'll only take a minute.
		[C] You'll be happy that you did it. Just go [Bb]over to your oven and shove your head in it.
		[F]Kill yourself.[Dm] Really, you should do it.
		There's[C] really nothing to it. Just [Bb]grab a mug and chuck a cup of lighter fluid.
	\end{highlightbar}
	
	\songsection{Verse 2}
	I sound un-empethatic. I sound mean and rude.
	Suicide is an epidemic and I don't wanna be misconstrued.
	Signs of depression go overlooked
	So if you're depressed then you need to book...
	
	\songsection{Bridge}
	A therapy session, talk about your depression
	And let a professional hear it.
	But if you search for moral wisdom
	In Katy Perry's lyrics, then...
	
	\pagebreak
	
	\begin{highlightbar}
		\songsection{Chorus}
		[F]Kill yourself.[Dm] It won't be painful
		[C] If you are able to [Bb]give a little kiss to an oncoming train,
		You'll [F]kill yourself.[Dm] It's over mull it
		[C] There's the trigger, pull it. [Bb]Get it through your head, "it" being a bullet.
	\end{highlightbar}
	
	\songsection{Verse 3}
	[F] Stick your tongue in a plu[Dm]g, suck a pipe of exha[Bb]ust,
	Make some toast in the tu[C]b, nail yourself to a cro[F]ss,
	Hold your breath till it's go[Dm]ne, drink a gallon of ma[Bb]ce,
	Be gay in Ira[C]n, let Oprah sit on your fa[(F)]ce.
	
	\songsection{Verse 4}
	Jump off of a bridge, skinny dip in a flood,
	Sky dive attached to a fridge, drink a Haitian guy's blood,
	Break into the zoo, give a tiger a shove,
	Eat a Phillips head screw, marry Courtney Love.
\end{guitar}

