\songtitle{Lemon Tree}{Fool's Garden}{1995}

\guitarchord{Em}
\guitarchord{Bm}
\guitarchord{Bflatm}
\guitarchord{Am}
\guitarchord{G}
\guitarchord{D}
\guitarchord{C/G}
\guitarchord{D7}
\guitarchord{A7}
\guitarchord{B}

\hfill\capoEN{1}

\begin{guitar}
	\songsection{Intro}{\footnotesize\begin{tabular}{l|l|l|l}
			Em & Bm & Em & Bm B$\flat$m \\
			Am & Bm & Em Bm & Em 
	\end{tabular}}

	\songsection{Verse 1}
	I'm [Em]sitting here in the [Bm]boring room.
\end{guitar}
	
\vspace{-2.875em} \hfill \strummingFourBeatsAndTwoMovementsPerBeat{bdbdbdbd}
\vspace{-0.125em} 
	
\begin{guitar}
	It's [Em]just another rainy Sunday [Bm]afternoon.
	I'm [Em]wasting my time, I got [Bm]nothing to do,
	I'm [Em]hanging around, I'm [Bm]waiting for you [Bbm]but
\end{guitar}

\vspace{-2.875em} \hfill \strummingFourBeatsAndTwoMovementsPerBeat{bdbdbdbb}
\vspace{-0.125em} 

\begin{guitar}
	[Am]Nothing ever happens[Bm] and I [Em]wonder.[Bm Em]{}
\end{guitar}

\vspace{-2.875em} \hfill \strummingFourBeatsAndTwoMovementsPerBeat{bdbdbdbb}\strummingFourBeatsAndTwoMovementsPerBeat{bdbdb.d.}
\vspace{-0.125em} 

\vspace{1em}
\begin{guitar}
	I'm driving around in my car.
	I'm driving too fast, I'm driving too far.
	I'd like to change my point of view.
	I feel so lonely, I'm waiting for you but
	Nothing ever happens and I wonder.
	
	\songsection{Chorus}
	I [G]wonder how, I [D]wonder why. 
	[Em]Yesterday you told me 'bout the [Bm]blue, blue sky.
	And [C/G]all that I can s[D]ee is just a yellow [G]lemon tree.[D7]{}
	I'm [G]turning my head [D]up and down.
	I'm [Em]turning, turning, turning, turning, [Bm]turning around.
	And [C/G]all that I can [A7]see is just another [D7]lemon tree.
	
	\songsection{Post Chorus}
	Sing: [Em]dab,[Bm] da da da da dabn [Em]di dab daaa,[Bm] da da da da [Bbm]dabn
	 [Am]Di dab daaa,[Bm] dab dibn di daa[Em|]o[Bm Em]{}
	
	\songsection{Verse 2}
	I'm sitting here. I miss the power.
	I'd like to go out. Taking a shower.
	But there's a heavy cloud inside my head.
	I feel so tired, put myself into bed while
	Nothing ever happens and I wonder.
	
	\songsection{Bridge}
	[Bm] Isolation - [Em]is not good for me.
	[D] Isolation - [G]I don't want to [B]sit on the lemon tree.
	
	\songsection{Verse 3}
	I'm [Em]steppin' around in the [Bm]desert of joy.
	[Em]Maybe anyhow I'll get a[Bm]nother toy [Bbm]and
	[Am]Everything will happen[Bm] and you [Em]wonder.[Bm Em]{}
	
	\songsection{Chorus}
	I [G]wonder how, I [D]wonder why. 
	[Em]Yesterday you told me 'bout the [Bm]blue, blue sky
	And [C/G]all that I can [D]see is just another [G]lemon tree.[D7]{}
	I'm [G]turning my head [D]up and down.
	I'm [Em]turning, turning, turning, turning, [Bm]turning around.
	And [C/G]all that I can [A7]see is just a yellow [D7]lemon tree. And I wonder, wonder...
	
	\songsection{Outro}
	I [G]wonder how, I [D]wonder why. 
	[Em]Yesterday you told me 'bout the [Bm]blue, blue sky
	And [C/G]all that I can s[D]ee ... (dip dip)
	And [C/G]all that I can s[D]ee ... (dip dip)
	And [C]all that I can [D7]see is just a yellow [G]lemon tree.
\end{guitar}