% based on: https://tabs.ultimate-guitar.com/tab/alestorm/nancy-the-tavern-wench-chords-1009572
\songtitle{Nancy the Tavern Wench}{Alestorm}{2008}

\adjustboxDefault{%
	\guitarchord{Bm}
	\guitarchord{D-3}
	\guitarchord{A}
	\guitarchord{Em}
	\guitarchord{Fsharp}
	\guitarchord{G-3}}
\capoEN{1}

\begin{spacing}{0.98}
\begin{guitar}
	\songsection{Intro}
	{\footnotesize\begin{tabular}{|l|l|l|l|}
			Bm & Bm & D & D \\
			A & A & Em & F$\sharp$ \\
			Bm & Bm & D & D \\
			G & A & Bm & Bm
	\end{tabular}} \optionalChord{(x2)}
	
	\songsection{Verse 1}
	I [Bm]know of a tavern, [A]not far from here,
	[G]Where you can get some [F#]mighty fine beer.
	The [Bm]company true, and the [A]wenches are pretty.
	It's the [G]greatest damn place in the [F#]whole of the city.
	If you're [Bm]lookin' for crewmates, you'll [A]sure find 'em there:
	[G]cutthroats and lowlifes and [F#]worse I should dare.
	Ol' [Bm]Nancy don't care who [A]comes to her inn.
	It's a [G]den of debauchery, [F#]violence and sin.
	
	\begin{highlightbar}
		\songsection{Chorus} \optionalChord{(x2)}
		So [Bm]come take a drink and [D]drown your sorrows,
		and [A]all of our fears will be [Em]gone till to[F#]morrow.
		[Bm]Have no regrets and [D]live for the day,
		in [G]Nancy's [A]harbour [Bm]cafe.
	\end{highlightbar}
	
	\songsection{Verse 2}
	If you're looking to go on a glorious quest,
	there's a man there who knows of an old treasure chest.
	For some pieces of eight and a tankard of ale
	he'll show ye the map and tell ye its tale.
	And then there's Nancy, the lovely barmaiden.
	She may be old, but her beauty ain't fadin'.
	Ol' Nancy don't care who comes to her inn.
	It's a den of debauchery, violence and sin.
	
	\begin{highlightbar}
		\songsection{Chorus} \songsnippet{So come take a drink and drown your sorrows, ...} \optionalChord{(x2)}
	\end{highlightbar}
	
	\songsection{Instrumental}
	
	\begin{highlightbar}
		\songsection{Chorus} \songsnippet{So come take a drink and drown your sorrows, ...} \optionalChord{(x2)}
	\end{highlightbar}\end{guitar}\end{spacing}