%source: I used chordify
\songtitle{Oh, the Joy!}{Rave The Reqviem}{2019(?)}

\adjustboxDefault{
\guitarchord{Dm}
\guitarchord{Bflat}
\guitarchord{C}
\guitarchord{Gm}
\guitarchord{F}}
\strummingTwoBeatsAndFourMovementsPerBeat{d.du.udu}

\begin{guitar}
	\songsection{Intro}
	[Dm Bb(muted)|]{} [Bb] Ah-[C]ah-ah-[Dm]ah-ah-[Gm]aah
	[Bb] Ah-[C]ah-ah-[Dm]aaah (ah-ah-ah-ah)
	
	\songsection{Verse 1}
	The [Dm]hole in your soul is growing [C]bigger by the [Dm]hour
	To [F]store the tears you [Bb]fought back and [F]proudly kept in[C]side
	It's [Dm]time to fight our way to heaven. [C]Lock and load your [Dm]guns.
	Now the [Bb]gates of Eden [F]open, Arma[Bb]geddon [F]has be[C]gun.
	
	And [F]all a[C]long we're singing
	
	\songsection{Chorus}
	[Dm]Blow, oh, [F]blow! Oh, [Bb]winds of [Dm]para[C]dise!
	As the [F]rivers of [Bb]blood of sinners [Dm]flow to our [C]delight.
	[Dm]Oh, the [F]joy! The [Bb]last day [Dm]has ar[C]rived!
	No more [Bb]suffering, no [C]more of sinners' [Dm]lies. Oh, [Gm]Lord!
	Come [Bb]morning, come [C]sunshine, come [Dm]light.
	
	\songsection{Verse 2}
	Only those pure in heart will see the kingdom come.
	You must trust my words. When sinners talk, you answer with your gun.
	We pave the way for paradise. We leave no stone unturned.
	No more mercy for the nonbelievers. Let the sinners burn.
	
	And all along we're singing
	
	\songsection{Chorus} \songsnippet{Blow, oh, blow! Oh, winds of paradise! ...}
	
	(Alright believers, one more time now)
	
	\songsection{Chorus} \songsnippet{Blow, oh, blow! Oh, winds of paradise! ...}
	
	Oh, [Gm]Lord!
	Come [Bb]mooorning, come [C]suuunshine, come [Dm]light
\end{guitar}