\songtitle{Slim Pickens Does The Right Thing And Rides The Bomb To Hell}{The Offspring}{2010}

\guitarchord{Dm}
\guitarchord{Bflat}
\guitarchord{F}
\guitarchord{C}
\guitarchord{Gm}

\begin{guitar}
	\songsection{Intro}
	{\footnotesize\begin{tabular}{l|l|l|l l}
			Dm & B$\flat$ & F & C & (x2)
	\end{tabular}}
	
	\songsection{Verse 1}
	[Dm]Take me for a [Bb]ride, I'm the [F]one you pushed a[C]side
	But it's coming back to you, yeah, it's coming back to you
	Run to the sound, take it back and double down
	Cause it's coming back to you, yeah, it's coming back to you (well)
	
	\songsection{Chorus}
	[Dm]Ah-ah-[Bb]ah, well, we're [F]pouring gaso[C]line
	So [Dm]dance around the [Bb]fire that we [F]once be[C]lieved in
	[Dm]Ah-ah-[Bb]ah, and we'll [F]never be the [C]same, now
	[Bb] Cause there's nothing left for [C]us to bleed
	[Bb] Give it up the champi[C]ons of greed
	[Bb] So come around and have a[C]nother round on [Dm]me
	[(Dm)]Dance, fucker, dance! Let the motherfucker burn!
	
	\songsection{Verse 2}
	Snake is in the grass while you're living in the past
	Sayin' whatcha gonna do? Yeah, whatcha gonna do?
	Earn never learn we'll be cheering while it burns
	And we're coming after you. Yeah, we're coming after you
	Slim Pickens, well, he does the right thing
	And he rides the bomb to hell. Yeah, he rides the bomb to hell
	Watch the pulse, it quickens after every little sting
	If you're gonna go to hell, drink it up you might as well
	
	\songsection{Bridge}
	[Bb] Are you really gonna [C]take it like that?
	[B]Riding on a missile with a [C]cowboy hat (and)
	\pagebreak
	\songsection{Chorus}
	Ah-ah-ah, well, the world is gonna end
	So dance around the fire that we once believed in
	Ah-ah-ah wanna tear it down again, now
	Cause there's nothing left for us to bleed
	Give it up the sons of anarchy
	So come around and have another round on me
	Dance, fucker, dance! Let the motherfucker burn!
	
	\songsection{Intrumental}
	
	\songsection{Bridge}
	Are you really gonna take it like that?
	Riding on a missile with a baseball bat (and)
	
	\songsection{Chorus}
	Ah-ah-ah, well, we're pouring gasoline
	So dance around the fire that we once believed in
	Ah-ah-ah, and we'll never be the same
	The takers and the liars that we all believed in
	Ah-ah-ah, well, we're going down in flames
	So dance around the fire, we dance around the fire
	Cause there's nothing left for us to bleed
	Give it up the champions of greed
	So come around and have another round on me
	
	\songsection{Outro}
	[(Dm)] (Hey! Hey!)
	[(Dm)]Dance fucker dance let the motherfucker burn!
\end{guitar}