\songtitle{Star of the County Down}{Cathal McGarvey}{$\sim$1900}
Melody: Van Morrison \& The Chieftains

\guitarchord{Em}
\guitarchord{G}
\guitarchord{D}
\guitarchord{C}

\begin{guitar}
	\songsection{Verse 1}
	Near [Em]Banbridge Town in the [G]County [D]Down
	One [Em]morning [C]last [D]July
	Down a [Em]boreen green came a [G]sweet cai[D]lín
	And she [Em]smiled as she [D]passed me [Em]by.
	She [G]looked so sweet from her [D]two bare feet
	To the [Em]sheen of her [C]nut brown [D]hair.
	Such a [Em]winsome elf, sure I [G]shook my[D]self
	For to [Em]see I was [D]really [Em]there.
	
	\songsection{Chorus}
	And from [G]Bantry Bay up to [D]Derry Quay
	and from [Em]Galway to [C]Dublin [D]Town
	No [Em]maid I've seen like the [G]fair cai[D]lín
	That I [Em]met in the [D]County [Em]Down.
	
	\songsection{Verse 2}
	As she onward sped, sure I scratched my head
	And I gazed with a feeling rare.
	And I said, says I, to a passer-by:
	"Who's the maid with the nut brown hair?"
	And he smiled at me and he said to me:
	"That's the gem of Ireland's crown.
	Young Rosie McCann from the banks of the Bann.
	She's the star of the County Down."
	
	\songsection{Chorus} \songsnippet{And from Bantry Bay up to Derry Quay...}
	
	\pagebreak
	
	\songsection{Verse 3}
	She had soft brown eyes with a look so shy
	And a smile like a rose in June.
	And she sang so sweet, what a lovely treat
	As she lilted an Irish tune.
	At the Lambuth dance I was in the trance
	As she whirled with the lads of the town
	And it broke my heart just to be apart
	From the star of the County Down.
	
	\songsection{Chorus} \songsnippet{And from Bantry Bay up to Derry Quay...}
	
	\songsection{Verse 4}
	At the Harvest Fair she'll be surely there
	So I'll dress in my Sunday clothes,
	With my shoes shone bright and my hat cocked right
	For a smile of the nut brown rose.
	No pipe I'll smoke, no horse I'll yoke
	Till my plough turns a rust coloured brown
	And a smiling bride by my own fireside
	Sits the star of the County Down.
	
	\songsection{Chorus} \songsnippet{And from Bantry Bay up to Derry Quay...}
\end{guitar}