\songtitle{Still Alive}{Jonathan Coulton}{2007}

\guitarchord{D}
\guitarchord{Bm}
\guitarchord{Em-2}
\guitarchord{A}
\guitarchord{Bflat}
\guitarchord{F}
\guitarchord{C}
\guitarchord{Gm}
\guitarchord{Dm}

\begin{guitar}
	\songsection{Verse 1}
	This was a tri[D]umph.[Bm]{}
	[D] I'm [Bm]making a [D]note here: [Bm]huge suc[D]cess.[Bm]{}
	It's [Em]hard to over[A]state my satis[D]faction.[Bm]{}
	[D ] [Bm]Aperture Sci[D]ence[Bm]{}
	[D] We [Bm]do what we [D]must be[Bm]cause we [D]can.[Bm]{}
	[Em]For the good of [A]all of us, except the [Bb]ones who are dead.
	
	\begin{highlightbar}
		\songsection{Chorus 1}
		But there's [F]no sense [C]crying over [Bb]every mis[F]take.
		You just [F]keep on [C]trying till you [Bb]run out of [F]cake.
		And the [Gm]science gets [C]done and you [F]make a neat [Dm]gun
		for the [Bb]people who a[A]re still al[D]ive.[Bm D Bm D Bm D Bm]{}
	\end{highlightbar}
	
	\songsection{Verse 2}
	I'm not even angry.
	I'm being so sincere right now.
	Even though you broke my heart and killed me.
	And tore me to pieces.
	And threw every piece into a fire.
	As they burned it hurt because I was so happy for you!
	
	\begin{highlightbar}
		\songsection{Chorus 2}
		Now these points of data make a beautiful line
		And we're out of beta, we're releasing on time.
		So I'm glad I got burned, think of all the things we learned
		For the people who are still alive.
	\end{highlightbar}
	
	\songsection{Verse 3}
	Go ahead and leave me.
	I think I prefer to stay inside.
	Maybe you'll find someone else to help you.
	Maybe Black Mesa.
	That was a joke, ha ha, fat chance.
	Anyway this cake is great; it's so delicious and moist.
	
	\begin{highlightbar}
		\songsection{Chorus 3}
		Look at [F]me still [C]talking when there's [Bb]science to [F]do.
		When I [F]look out [C]there it makes me [Bb]glad I'm not [F]you.
		I've ex[Gm]periments to [C]run, there is [F]research to be [Dm]done
		On the [Bb]people who [A]are still al[D]ive.[Bm D Bm D Bm D Bm]{}
	\end{highlightbar}
	
	\songsection{Outro}
	And be[D]lieve me I [Bm]am still a[D]live.[Bm]{}	
	I'm doing science and I'm still alive.
	I feel fantastic and I'm still alive.
	While you're dying I'll be still alive.
	And when you're dead I will be still alive.
	Still alive. Still alive.
	
\end{guitar}