\songtitle{You're Gonna Go Far, Kid}{The Offspring}{2008}

\guitarchord{Am}
\guitarchord{F}
\guitarchord{C}
\guitarchord{G}
\guitarchord{Dm}
\guitarchord{Fsus2}
\guitarchord{Dm7}
\guitarchord{E}

\begin{guitar}
	\songsection{Verse 1}
	[Am]Show me how to lie. You're getting [F]better all the time
	And turning [C]all against the one is an [G]art that's hard to teach.
	
	Another clever word sets off an unsuspecting herd
	And as you step back into line a mob jumps to their feet.
	
	Now, dance, fucker, dance. Man he never had a chance
	And no one even knew it was really only you.
	
	\songsection{Pre-Chorus}
	And now you [F]steal away,
	Take him [Dm]out today.
	Nice [Fsus2]work you did,
	You're gonna go [Dm7]far, kid.[E]{}
	
	\begin{highlightbar}
		\songsection{Chorus}
		With a [Am]thousand lies and a [F]good disguise
		Hit 'em [C]right between the eyes, hit 'em [G]right between the eyes.
		When you [Am]walk away, nothing [F]more to say
		See the [C]lightning in your eyes, see 'em [G]running for their lives.[Am G]{}
	\end{highlightbar}
	
	\songsection{Verse 2}
	Slowly out of line and drifting closer in your sights.
	So play it out, I'm wide awake. It's a scene about me.
	
	There's something in your way and now someone is gonna pay
	And if you can't get what you want, well, it's all because of me.
	
	Now, dance, fucker, dance. Man I never had a chance
	And no one even knew it was really only you
	
	\songsection{Pre-Chorus}
	And now you'll lead the way,
	Show the light of day.
	Nice work you did,
	You're gonna go far, kid. (Trust deceived)
	
	\begin{highlightbar}
		\songsection{Chorus}
		With a [Am]thousand lies and a [F]good disguise
		Hit 'em [C]right between the eyes, hit 'em [G]right between the eyes.
		When you [Am]walk away, nothing [F]more to say
		See the [C]lightning in your eyes, see 'em [G]running for their lives.
	\end{highlightbar}
	
	\songsection{Instrumental}
	{\footnotesize\begin{tabular}{|l|l|l|l|}
			E  & F & C & E \\
			Am & F & C & G
	\end{tabular}}
	
	\songsection{Verse 3}
	Now, [Am]dance, fucker, dance. He [F]never had a chance
	And [C]no one even knew it was [G]really only you
	So, dance, fucker, dance. I never had a chance,
	It was really only you.
	
	\begin{highlightbar}
		\songsection{Chorus} \songsnippet{With a thousand lies and a good disguise...}
		
		\songsection{Chorus}
		Clever alibis, Lord of the flies
		Hit 'em right between the eyes, hit 'em right between the eyes.
		When you walk away, nothing more to say
		See the lightning in your eyes, see 'em running for their lives.
	\end{highlightbar}
\end{guitar}